Progress Report on the ``Adult Database'' analysis

### 2009-11-11 report/paper.tex
Add problem identification.

Each entry is composed by a set of 14 attributes and a class, identifying
persons who gain more or less than 50K. The attributes and types are:

@@

@@

\section{Future Work}

>>>>

Each entry is composed by a set of 14 attributes and two classes, identifying
persons who gain more or less than 50K dollars per year. The attributes and types are:

@@

Deducing from the previous section, this is a classification problem. Given an adult
with the mentioned attributes we want to classify him into one of the following groups:
one gains more than 50000 dollars per year, the other group does not.

One important objective in classifying things is to understand why the given object
is put under one class and not in another, that is, we want to understand what social characteristics
allows one person to gain more than someone else, if the sex is important, the education level,
the race and what factors are less important.

Given a specific set of persons from a certain society and from a certain time we could then
learn what contributes to a person's social standing and, as we all know, money is an important
metric in that department. We could, for example, learn if the race affects the persons success and if
that society discriminates certain races.

Understanding what affects the money gained through an year can gives a lot of information
concerning society's behaviors.

@@

\section{Work plan}
